Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-05-30 docs/paper/paper.Rmd
figure 1 and 3 in place

---
title: Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble
preprint: false
author: 
  - name: Sam Abbott
    affiliation: 1
    corresponding: true
    email: sam.abbott@lshtm.ac.uk
affiliation:
  - code: 1
    address: Cold Spring Harbor Laboratory, One Bungtown Road Cold Spring Harbor, NY 11724
abstract: > 
  We made the best model. It is both simple and amazing.
bibliography: library.bib
output:
  rticles::peerj_article: default
  bookdown::pdf_book:
    base_format: rticles::peerj_article # for using bookdown features like \@ref()
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = TRUE,
  echo = FALSE,
  message = FALSE,
  cache = TRUE
)
```

@@

```{r relative-interval-score}
relative_interval_score <- scores |>
  copy() |>
  setorderv(c(
    "location", "target_end_date", "horizon", "quantile", "model"
  )) |>
  DT(,
    relative_interval_score := interval_score / shift(interval_score),
    by = c("location", "target_end_date", "horizon", "quantile")
  ) |>
  DT(model %in% "Surrogate")
```

@@

```{r vis-forecasts, fig.height = 9, fig.width = 9, fig.cap = "Forecasts of notified test positive cases (per 10,000 population) by epidemiological week in the Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom,  by forecast horizon (one to four weeks). Incidence rates are shown on a log scale. 30%, 60%, and 90% credible intervals are shown. The black line and points are the notified cases as of the date of data extraction rather than those available at the time."}
locs <- c("United Kingdom", "Germany", "Slovakia", "Italy", "Poland", "Greece")

@@

```{r plot-coverage}
hlines <- data.table(
  range = paste0(ranges, "% interval"), nominal = ranges / 100
)

plot_cov_levels <- ggplot(coverage) +
  aes(
    x = horizon, y = coverage, colour = model, group = interaction(range, model)
  ) +
  geom_line() +
  geom_point() +
  geom_hline(
    data = hlines, aes(yintercept = nominal, x = NULL), linetype = "dashed"
  ) +
  scale_colour_brewer(palette = "Dark2") +
  scale_y_continuous(labels = percent) +
  facet_wrap(vars(range), ncol = 1) +
  theme_scoringutils() +
  labs(
     y = "Proportion of data within forecast interval",
     x = "Forecast horizon (weeks)",
     col = "Model"
  )

plot_cov_quantile <- scores |>
  summarise_scores(by = c("model", "quantile", "horizon")) |>
  plot_quantile_coverage(scores) +
  aes(col = model) +
  scale_colour_brewer(palette = "Dark2") +
  facet_wrap(vars(horizon)) +
  labs(col = "Model")

plot_interval_score <- relative_interval_score |>
  geom
```
# Discussion {-}

>>>>

---
title: Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble
preprint: false
author: 
  - name: Sam Abbott
    affiliation: 1
    corresponding: true
    email: sam.abbott@lshtm.ac.uk
affiliation:
  - code: 1
    address: Cold Spring Harbor Laboratory, One Bungtown Road Cold Spring Harbor, NY 11724
abstract: > 
  We made the best model. It is both simple and amazing.
bibliography: library.bib
output:
  rticles::peerj_article: default
  bookdown::pdf_book:
    base_format: rticles::peerj_article
    extra_dependencies: ["float"]
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = TRUE,
  echo = FALSE,
  message = FALSE,
  cache = TRUE,
  messages = FALSE,
  warnings = FALSE
)
```

@@

```{r relative-interval-score}
cols <- c("location", "target_end_date", "horizon", "range", "model")
relative_interval_score <- scores |>
  copy() |>
  setorderv(cols) |>
  DT(, c(..cols, "interval_score")) |>
  unique() |>
  DT(,
    relative_interval_score := interval_score / shift(interval_score),
    by = c("location", "target_end_date", "horizon", "range")
  ) |>
  DT(model %in% "Surrogate")
```

@@

```{r vis-forecasts, fig.cap = "Forecasts of notified test positive cases (per 10,000 population) by epidemiological week in the Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom,  by forecast horizon (one to four weeks). Incidence rates are shown on a log scale. 30\\%, 60\\%, and 90\\% credible intervals are shown. The black line and points are the notified cases as of the date of data extraction rather than those available at the time.", out.width = "95%", fig.height = 12, fig.width = 9}
locs <- c("United Kingdom", "Germany", "Slovakia", "Italy", "Poland", "Greece")

@@

```{r plot-coverage, fig.height = 9, fig.width = 9, out.width = "95%"}
hlines <- data.table(
  range = paste0(ranges, "% interval"), nominal = ranges / 100
)

plot_cov_levels <- ggplot(coverage) +
  aes(
    x = horizon, y = coverage, colour = model, group = interaction(range, model)
  ) +
  geom_line() +
  geom_point() +
  geom_hline(
    data = hlines, aes(yintercept = nominal, x = NULL), linetype = "dashed"
  ) +
  scale_colour_brewer(palette = "Dark2") +
  scale_y_continuous(labels = percent) +
  facet_wrap(vars(range), ncol = 1, scales = "free_y") +
  theme_scoringutils() +
  labs(
     y = "Proportion of data within forecast interval",
     x = "Forecast horizon (weeks)",
     col = "Model"
  )

plot_cov_quantile <- scores |>
  summarise_scores(by = c("model", "quantile", "horizon")) |>
  plot_quantile_coverage(scores) +
  aes(col = model) +
  scale_x_continuous(labels = percent) +
  scale_y_continuous(labels = percent) +
  scale_colour_brewer(palette = "Dark2") +
  guides(col = guide_none()) +
  facet_wrap(vars(horizon)) +
  labs(col = "Model", y = "Percent of observations below quantile")

plot_interval_score <- relative_interval_score |>
  copy() |>
  DT(,
    .(relative_interval_score = median(relative_interval_score)),
    by = c("horizon", "range")
  ) |>
  ggplot() +
  aes(x = range / 100, y = relative_interval_score, col = as.factor(horizon)) +
  geom_hline(yintercept = 1, linetype = 2) +
  geom_point(size = 1.2) +
  geom_line(alpha = 0.8) +
  scale_x_continuous(labels = percent) +
  scale_y_continuous(trans = "log", breaks = seq(1, 4, by = 0.2)) +
  scale_colour_brewer(palette = "Accent") +
  theme_scoringutils() +
  labs(
    x = "Quantile", y = "Median relative interval score",
    col = "Forecast horizon (weeks)"
  )

(((plot_cov_levels /
  plot_interval_score)  +
  plot_layout(heights = c(3, 1), guides = "collect")
) |
  plot_cov_quantile) +
  plot_layout(guides = "collect", widths = c(1, 2)) +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.box="vertical", legend.margin = margin()
  )
```

# Discussion {-}
